The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
update renders, add section numbers

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
   # github_document
  bookdown::pdf_document2:
     number_sections: false
  #bookdown::word_document2:
   # reference_docx: template.docx
bibliography: ../references/knitcite.bib
---

@@

# Scale in multilayer networks in practice: case study results and discussion

>>>>

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
  # github_document
  bookdown::pdf_document2:
     number_sections: true
  # bookdown::word_document2:
  #   reference_docx: template.docx
bibliography: ../references/knitcite.bib
---

@@

# Scale in multilayer networks in practice: case study results and discussion
<!-- TODO: Add intro/general to results? with mention figures are means of inds-->
